Screening of airborne radioxenon measurements for Nuclear-Test-Ban Treaty verification

### 2022-10-21 paper/paper.tex
Added time series plot and accompanying text.

>>>>

To grant some intuition about the time dependence of the variability of the optimized emissions, the time series of the weights are plotted for different values of the regularization parameter (see \cref{fig: optimized weights timeseries lambda=10}, \cref{fig: optimized weights timeseries lambda=1}, \cref{fig: optimized weights timeseries lambda=0.1}). At first glance, all time series look erratic. Looking at the measured emission data in \cite{Ringbom2021}, the data is seemingly also erratic. This can support the claim that our optimized emissions could be realistic, however proper time series analysis is still needed to extract firm conclusions. At the same time, we see that all time series for the optimized weights look similar (ignoring the scale differences). This can be expected, as all optimized solutions try to fit the same data but are hindered in different amounts by their respective regularization parameter.

\begin{figure}
	\centering
	\begin{minipage}{.31\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../plots/Optimized_weights_timeseries_lambda10.png}
		\caption{Time series of the optimized weights $W$, using a large regularization parameter $\lambda=10$.}
		\label{fig: optimized weights timeseries lambda=10}
	\end{minipage}\hfill
	\begin{minipage}{.31\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../plots/Optimized_weights_timeseries_lambda1.png}
		\caption{Time series of the optimized weights $W$, using a medium regularization parameter $\lambda=1$.}
		\label{fig: optimized weights timeseries lambda=1}
	\end{minipage}\hfill
	\begin{minipage}{.31\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../plots/Optimized_weights_timeseries_lambda01.png}
	\caption{Time series of the optimized weights $W$, using a small regularization parameter $\lambda=0.1$.}
	\label{fig: optimized weights timeseries lambda=0.1}
	\end{minipage}
\end{figure}
